Merging merges, more or less

### 2015-03-04 2015mergingmerges/section/02-Machines.tex
remove progs

\subsection{Conversion of combinators}
The combinators from section~\ref{s:Combinators} can be converted to these DFAs quite easily.

Well, do it.
I'm still not sure, maybe just showing the pictures would be better.

>>>>

\subsection{Combinators}
Many interesting combinators can be described using these machines.
In figures 1-4, the machines for some important combinators are given.
To reduce clutter, these figures omit labels for @Unit@ transitions.

While writing combinators in this form is neither pleasant nor pretty, it only needs to be done once.
The implementation contains more combinators such as group by, append and indices of segment lengths.

\input{figures/Combinators.tex}

\subsection{Code extraction}

Extracting imperative code from these machines is quite straightforward.
Variables are created for each 
Each state is converted to a basic block and given a unique identifier as its label.
